Left-linear rules in adhesive categories

### 2024-02-14 icalp/fusione.tex
minori

The paper has the following structure. 
Section~\ref{sec:ade} recalls the basic 
definitions of DPO rewriting for $\mathcal{M}$-adhesive categories. 
Section~\ref{sec:equi} presents the key novelties of our proposal,
first introducing the classical notion of independence and 
a novel axiomatic notion of switchability, further showing that the
former fails to imply the latter for left-linear rewriting systems.
We then define well-switching systems,
and prove that all the classical results holding for linear rewriting systems
can be recovered for such a class of left-linear ones.
Finally, Section~\ref{conclusions} wraps up the paper and 
offers some thoughts on possible directions for future work.
The appendixes collect additional data, recalling basic results on
adhesive categories (Appendix~\ref{app:ade}), introducing and 
proving properties for \emph{strong enforcing} rewriting systems, a class of systems where sequential independence is well-behaved
(Appendix~\ref{app:fill}), and giving the proofs of the main 
results of our work (Appendix~\ref{omitted}).

>>>>

The paper has the following structure. 
Section~\ref{sec:ade} recalls the basic 
definitions of DPO rewriting for $\mathcal{M}$-adhesive categories. 
Section~\ref{sec:equi} presents the key novelties of our proposal,
first introducing the classical notion of independence and 
a novel axiomatic notion of switchability, further showing that the
former fails to imply the latter for left-linear rewriting systems.
We then define well-switching systems,
and prove that all the classical results holding for linear rewriting systems
can be recovered for such a class of left-linear ones.
Finally, Section~\ref{conclusions} wraps up the paper and 
offers some thoughts on possible directions for future work.
The appendixes collect additional data, recalling basic results on
adhesive categories (Appendix~\ref{app:ade}), introducing and 
proving properties for \emph{strong enforcing} rewriting systems, a class of systems where the local Church-Rosser Theorem holds
(Appendix~\ref{app:fill}), and giving the proofs of the main 
results of our work (Appendix~\ref{omitted}).
